Python as a machine learning language: experiences from the scikit-learn project

### 2013-05-03 paper.tex
weaken PyPy "promise"

As much as possible is implemented in ``pure'' Python,
to avoid the compile-edit-debug cycle needed for Cython
and to keep the codebase readable for as large an audience as possible.
However, since the speed of the current Python implementation
is not sufficient for numeric programming
and NumPy's vector operations are not appropriate for all use cases
(among other factors, because they often have linear space requirements),
some of the core algorithms have to be implemented in Cython.\footnote{
  The only Python implementation currently supported by scikit-learn
  is the reference implementation, CPython.
  The alternative Python implementation PyPy \citep{bolz2009tracing}
  promises to solve this problem by JIT compilation,
  but does not yet interoperate with NumPy and SciPy.
}
Examples include the aforementioned $k$-means implementation,
stochastic gradient descent for linear models
and some graph-based clustering algorithms.

>>>>

As much as possible is implemented in ``pure'' Python,
to avoid the compile-edit-debug cycle needed for Cython
and to keep the codebase readable for as large an audience as possible.
However, since the speed of the current Python implementation
is not sufficient for numeric programming
and NumPy's vector operations are not appropriate for all use cases
(among other factors, because they often have linear space requirements),
some of the core algorithms have to be implemented in Cython.\footnote{
  The only Python implementation currently supported by scikit-learn
  is the reference implementation, CPython.
  The alternative Python implementation PyPy \citep{bolz2009tracing}
  promises to alleviate this problem by JIT compilation,
  but does not yet interoperate with NumPy and SciPy.
}
Examples include the aforementioned $k$-means implementation,
stochastic gradient descent for linear models
and some graph-based clustering algorithms.
